\chapter[Optimization of negative stage bias potential]{Optimization of negative stage bias potential for faster imaging in large-scale electron microscopy}
\label{chap:2}

% Abstract
\begin{abstract}
    Large-scale electron microscopy (EM) allows analysis of both tissues and macromolecules in a semi-automated manner, but acquisition rate forms a bottleneck. We reasoned that a negative bias potential may be used to enhance signal collection, allowing shorter dwell times and thus increasing imaging speed. Negative bias potential has previously been used to tune penetration depth in block-face imaging. However, optimization of negative bias potential for application in thin section imaging will be needed prior to routine use and application in large-scale EM. Here, we present negative bias potential optimized through a combination of simulations and empirical measurements. We find that the use of a negative bias potential generally results in improvement of image quality and signal-to-noise ratio (SNR). The extent of these improvements depends on the presence and strength of a magnetic immersion field. Maintaining other imaging conditions and aiming for the same image quality and SNR, the use of a negative stage bias can allow for a 20-fold decrease in dwell time, thus reducing the time for a week long acquisition to less than \SI{8}{\hour}. We further show that negative bias potential can be applied in an integrated correlative light electron microscopy (CLEM) application, allowing fast acquisition of a high precision overlaid LM-EM dataset. Application of negative stage bias potential will thus help to solve the current bottleneck of image acquisition of large fields of view at high resolution in large-scale microscopy.
\end{abstract}

% Published as footnote
\blfootnote{This chapter has been published as: \fullcite{lane2021optimization}.}
\clearpage


% Sections
\input{chapter-2/sec-1_intro}
\input{chapter-2/sec-2_results}
\input{chapter-2/sec-3_discussion}
\input{chapter-2/sec-4_methods}
\input{chapter-2/sec-A_supp}


% References
\printbibliography[title={References}]
