\chapter*{Acknowledgments}
\addcontentsline{toc}{chapter}{Acknowledgments}
\setheader{Acknowledgments}
% Reset footnote counter
\setcounter{footnote}{0} 


This thesis would not exist if not for the existence of many people. Chief among them is my promotor, Jacob, who granted me the opportunity to work on this project and whose trust and support allowed me to see it to the end. I feel extremely fortunate that we shared a common vision for this project, and that this thesis can serve as a culmination of that vision. (Although if I have learned anything in 4-5 years of working at a university, it is that there is always more to be done.\footnote{Provided there is funding.}) Many thanks also to my co-promotor, Elizabeth, as well as Pieter, Kees, and Daan for all the feedback during work discussions and in guiding my research.

I could not have chosen a more pleasant and supportive environment in which to do my PhD, and for that I must thank the good people of the MInT group (formerly CPO) for this luxury. Luc, Aya, and Cristiano (aka the Italian Falcon), some of the best office mates I could have asked for. I always felt comfortable bouncing ideas off of you, although I have to admit I found it mildly frustrating to share an office with someone whose English is better then mine, Luc. 
Yoram and Mathijs, co-founders of the High Tree Gang, it has been such a privilege to work (and on very very rare occasions, not work) alongside you guys throughout the years---you not only improved the quality of my research, but made it much more enjoyable in the process. Thanks also to Aditi and Wilco who were pivotal resources in the early days before I knew anything, and on Friday evenings when it was time to forget some things.

Many thanks to Vidya, Nicö, Laura, Xin, and Marco for all the interesting and insightful chats around the coffee table, as well as for hosting an abundance of dinner parties. Your affection for cooking amazing food is outdone only by your hospitality (and mine and Marco’s appetite). 
Arent and C\'elina, thank you for teaching me elementary biology and the literalness of the Dutch language. If not for you guys I would not know that octopus eyes have a superior design (nerve cells \textit{behind} the retina $\longrightarrow$ no blindspot) or that pie is an all-encompassing term for anything made out of flour, eggs, butter, and sugar. 
D.\ B.\ Boltje: stressed, depressed, and always well-dressed. I'm still amazed that you basically arrived at my Proposition 8 organically and without any prompting---you always brighten my day. 
Ernest, thanks to your knowing many things and affable demeanor, you have become my go-to person for all things science-related and unrelated. Thanks as well for translating my summary to Dutch. I did not bother reverse-translating it, so I hope you did not put anything embarrassing in there\ldots

I was also fortunate to have supervised and worked with a number of dedicated bachelor and master students: Isabel, Daan, Nahum, Laurent, Simon, Marnix, and Luuk. The fact that your names are scattered elsewhere throughout this thesis shows that your work was not only instrumental in addressing some of our lab’s research goals but also gave a little bump to mankind’s collective understanding of how the world works (a little grandiose perhaps, but technically true). Luuk---my only master student, and largely responsible for Chapter \ref{chap:4}---thanks for all the hard work, ingenuity, and, most importantly, for making it enjoyable. I wish you the best of luck in your PhD and wish all my former students the best in their future endeavors. 

Not a single experiment I conducted would have been possible without support from our amazing technical and administrative staff: Johan, Ruud, Carel, Han, Youp, Martin, Anjella, Yvonne, Malee, and Anneloes. A huge thanks to Dustin (who in part led me to the Netherlands in the first place) for not only knowing every pin layout of every circuit board on every instrument, but for sharing in our frustration when something broke. Nothing like getting your microscope fixed while commiserating.
The same can be said regarding my collaborators Ben, Anouk, Peter, and Ahmad (from UMCG); Nalan, Elisa, and Judith (UMCU); Lennard (LUMC); and Andries, \'Eric, and Marre (Delmic).

Thanks also to my friends outside the soviet-era slab of concrete. I owe a big thanks to all the guys at Squash Delft for keeping me active through the years. Chetan, you have been my guiding light, my brother from an Indian mother. Part of me wishes we had actually learned Dutch in Dutch class, but I guess it wouldn’t have been as fun that way.
Thanks as well to my housemates over the past couple years, Stefan, Seraphina, Marina, Lotte, and Ruta, for ensuring I have a nice place to call home. Marina, I find myself missing our late night nanobiology chats, but I am sure you will do great things with phages in New Zealand.
To my friends back home: John, Kyle, Claire, I am so happy every time we are able to get back together, especially when exploring new places. That mostly applies to John... Kyle and Claire, you could have visited more. Tyler, you never visited, so that makes you the worst :)
And of course all of this would have been extra impossible without the love and support from my family. My time in Delft has certainly been filled with happy moments, but painful ones as well. For being there for me through the good times and the rough patches, Mom, Dad, Michelle, and Cara, I love you guys and I owe it all to you!
